---
title: "Midterm 1"
output: pdf_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

# load all of our libraries that we are going to use

library(stargazer)
library(psych)
library(mediation)
library(janitor)
library(haven)
library(arm)
library(tidyverse)

```

```{r, load data}

# Load Data in, and select only what we need to do our regressions

all_data <- read_dta("dataverse_files/replicationdata.dta") %>% 
  clean_names() %>% 
  select(
    scd_brad_self_report1_mean, 
    scd_brad_vid_manip_all_mean,
    anxcond3,
    anxcond, 
    immigration, 
    storycond)


```

# Abstract

This document is the culmination of the first half of the semester's studies in replicating published journal articles. In this document, I have replicated Table 1, Figure 2, and Figure 3 from the article “Physiological arousal and political beliefs."

Additionally, my main extension is that I have re-run the regressions for Table 1 and figure 3 using a bayesian approach, instead of the frequentist approach used in the paper. 

There are some differences between these two approaches. The Bayesian approach to linear regression returns a distribution for potential values that coefficients can take on, while the frequentist simply gives a point estimate with some estimate for standard error.

This Bayesian approach is helpful: it gives us another route to check the robustness of our model (indeed, the two estimates approach each other as the sample size appraoches infinity) and it allows us to inform the model about the expected value of each of the coefficients through a prior distribution. 

Ultimately, the regressions run both ways reveal that the model is still robust: the coefficients in the two estimates (before and after mediation) are still significant, and are very close to one another. 

\newpage

# Table 1

```{r table 1, results='asis'}

# select only the neutral and anxiety conditions

noRelaxCond <- filter(all_data, anxcond3 > 0)

# (1) perform frequentist linear regression on the conductance value
# while filling out the report, using the type of video used. 
# note that this is done after eliminating the neutral data

m <- lm( data = noRelaxCond, formula = scd_brad_self_report1_mean ~ anxcond) 

# (2) perform frequentist linear regression on the feelings towards 
# immigrants (scored using some combination of the data), using 
# the type of immigration story used, the type of video used, and 
# the conductance levels while filling out the report
# note that this is done after eliminating the neutral data

y <- lm( data = noRelaxCond, immigration ~ storycond + anxcond + scd_brad_self_report1_mean) 

# throw this into a table

stargazer(m, y, header = FALSE,
          omit.stat = c("f","ser"), 
          covariate.labels = c("Story Condition",
                               "Anxiety Manipulation",
                               "Skin Conductance Reactivity when answering questions",
                               "Constant"),
          dep.var.labels = c("Skin Conductance Reactivity", "Immigration Preferences"))

```

Here it should be noted that there are some problems with this preceding table. Namely, the standard errors in the chart do not match up with their appropriate significance level. The 0.232 coeffecient in model 2, for example, is listed as significant at the 0.05 level, instead of the 0.1 level. Do not be tricked by this error in the software. 

\newpage

# Figure 2

Means of skin-conductance reactivity by video condition. 95% confidence intervals are show surrounding the mean.



```{r, figure 2}

# figure 2

# select only the data that is the type of video watched and the 
# value of the skin conductance, and make sure that they are all
# useable values (no NAs)

dta_small <- select(all_data, scd_brad_vid_manip_all_mean, anxcond3) %>%
  filter(!is.na(anxcond3), !is.na(scd_brad_vid_manip_all_mean)) %>% 
  mutate(anxcond3_str = ifelse(anxcond3 == 0, "Relax", ifelse(anxcond3 == 1, "Neutral", "Anxiety")))

# plot these, with error bars (that is what mean_se is for)
# look here for more direction:
# https://stackoverflow.com/questions/38599335/
# how-to-add-standard-error-bars-to-a-box-and-whisker-plot-using-ggplot2
# but place the link all on one line

ggplot(dta_small, aes(x = anxcond3_str, y = scd_brad_vid_manip_all_mean)) + 
  theme_minimal() +
  stat_summary(fun.y=mean, geom="point", size=2) + 
  stat_summary(fun.data = mean_se, geom = "errorbar") + 
  labs(x = "Anxiety Condition Treated", y = "Skin Conductance Reactivity while watching video" ) 



```



\newpage

# Figure 3. 

Causal mediation plot. Treatment is anxiety video manipulation (compared to neutral condition), Mediator is skin conductance reactivity when answering immigration questions, Outcome is composite variable of immigration preferences.

Horizontal lines represent 90% confidence intervals for estimates.

```{r, figure 3}

# Causal Mediation Plot

# Mediation Analysis

# basically used to measure the actual effect of the treatment, getting rid
# of the mediator variable (in this case, the conductance)

m.out<-mediate(m,y, sims=500, treat="anxcond", mediator="scd_brad_self_report1_mean", dropobs=TRUE, boot=TRUE, conf.level=.90)

plot(m.out, labels=c("ACME\n(Physiological \nReactivity)", "Direct Effect \n(Anxiety)", "Total Effect"), cex.axis = 0.6) 



```


\newpage

# Table 1, extended

These correspond to the output to calls to a bayesian regression, same as figure 1.


```{r, extension table 1, results = 'asis'}

noRelaxCond <- filter(all_data, anxcond3 > 0)

# re-run the regressions above, but with a bayesian approach instead of a 
# frequentist approach

m_default_prior <- bayesglm( data = noRelaxCond, formula = scd_brad_self_report1_mean ~ anxcond) 

y_default_prior <- bayesglm( data = noRelaxCond, immigration ~ storycond + anxcond + scd_brad_self_report1_mean) 

# display summary results for these two regressions (ideally this would)
# be formatted better

summary(m_default_prior)
summary(y_default_prior)



```
\newpage

This is a graphical representation of the coefficients of the bayesian linear regression.


```{r, plot bayes m}


# throw these into plots

coefplot(m_default_prior)

```

\newpage

This is a graphical representation of the coefficients of the bayesian linear regression.

This shows what the coeffecients are, and how large the error bound is on them.

These error bars are actually quite large, however, they are still significant to a similar degree as the previous results. 

```{r, plot bayes y}


# throw these into plots

coefplot(y_default_prior)

```

\newpage

# Figure 3, extended

Causal mediation plot. Treatment is anxiety video manipulation (compared to neutral condition), Mediator is skin conductance reactivity when answering immigration questions, Outcome is composite variable of immigration preferences.

Horizontal lines represent 90% confidence intervals for estimates.

The extension is that this analysis was performed with bayesian linear regression, instead of frequentist linear regression. Ultimately, the values found her coincide closely with the values computed from the frequentist analysis, and thus demonstrate a robustness of the model.

```{r, extension, figure 3}

# re-run Mediation Analysis, this time with the bayesian regressions

m.out<-mediate(m_default_prior,y_default_prior, sims=500, treat="anxcond", mediator="scd_brad_self_report1_mean", dropobs=TRUE, boot=TRUE, conf.level=.90)

plot(m.out, labels=c("ACME\n(Physiological \nReactivity)", "Direct Effect \n(Anxiety)", "Total Effect"), cex.axis = 0.6) 

```
\newpage

# Bibliography

Hlavac, Marek (2018). stargazer: Well-Formatted Regression and Summary Statistics Tables.
 R package version 5.2.2. https://CRAN.R-project.org/package=stargazer 

Renshon, Jonathan, Jooa Julia Lee, and Dustin Tingley. “Physiological arousal and political beliefs.” Political Psychology36.5 (2015): 569-585.


